### 2023-04-21 chapter2/chapter2_supporting.tex
Fixed some issues with dangling hline commands not preceded by \\
Swapped order of score and substitution figures
Added regions figure to chapter 2 supplement
Added U test calculation result to caption

@@

\begin{landscape}
\footnotesize
\begin{longtable}{|l|l|l|l|l|l|}
\caption{\textbf{Features and their definitions.}}
\label{stable:features}
% Start first head
\hline
\textbf{Feature ID}    & \textbf{Feature name}                                                            & \textbf{Group name}                                                & \textbf{Range} & \textbf{Description}                                                                                                             & \begin{tabular}[c]{@{}l@{}}\textbf{Changes from}\\\textbf{Zarin \textit{et al.}}~\cite{Zarin2019}\end{tabular}
\endfirsthead

@@

\begin{landscape}
\footnotesize
\begin{longtable}{|l|l|}
\caption{\textbf{Feature regular expresions.}}
\label{stable:regexes}
% Start first head
\hline
\textbf{Feature ID}    & \textbf{Regular expression}
\endfirsthead

>>>>

\begin{figure}[h!]
\includegraphics[width=\textwidth]{regions/out/regions.png}
\centering
\caption{\textbf{Summary statistics of disorder and order regions.}
\textbf{(A)} Distribution of mean length of regions. \textbf{(B)} Boxplot of the sums of the average amino acid and indel substitution rates in the disorder and order regions. The substitution rates are significantly greater in the disorder regions than in the order regions ($p < 1 \times 10^{-10}$, Mann-Whitney \textit{U} test).}
\label{sfig:regions}
\end{figure}

@@

\begin{landscape}
\footnotesize
\begin{longtable}{|l|l|l|l|l|l|}
\caption{\textbf{Features and their definitions.}}
\label{stable:features}
% Start first head
\\ \hline
\textbf{Feature ID}    & \textbf{Feature name}                                                            & \textbf{Group name}                                                & \textbf{Range} & \textbf{Description}                                                                                                             & \begin{tabular}[c]{@{}l@{}}\textbf{Changes from}\\\textbf{Zarin \textit{et al.}}~\cite{Zarin2019}\end{tabular}
\endfirsthead

@@

\begin{landscape}
\footnotesize
\begin{longtable}{|l|l|}
\caption{\textbf{Feature regular expressions.}}
\label{stable:regexes}
% Start first head
\\ \hline
\textbf{Feature ID}    & \textbf{Regular expression}
\endfirsthead
